The development of infants' responses to mispronunciations: A Meta-Analysis

### 2020-09-24 VonHolzenBergmann_MPMetaAnalysis.Rmd
third round of reviews response

An *increase* in mispronunciation sensitivity with age is predicted by a maturation from holistic to more detailed phono-lexical representations and has been supported by several studies [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010]. The first words that infants learn are often not similar sounding [e.g. mama, ball, kitty; @CharlesLuce1995] and encoding representations for these words using fine phonological detail may not be necessary. According to PRIMIR [@Curtin2007; @Werker2005] infants' initially episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task. This argument is supported by the results of @Mani2010kepstups, who found that 12-month-old infants with a larger vocabulary showed a greater sensitivity to vowel mispronunciations than infants with a smaller vocabulary.

@@

The first set of questions concerns how infants' sensitivity is modulated by different kinds of mispronunciations. Following on the above example, some experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level, or *mispronunciation size* (i.e. 1-feature, 2-features, 3-features), finding that infants are more sensitive to larger mispronunciations (3-feature-changes) than smaller mispronunciations (1-feature changes) for both consonant [@White2008; @Bernier2017; @Tamasi2016] and vowel [@Mani2011] mispronunciations, known as graded sensitivity. This also has consequences for understanding the developmental trajectory of mispronunciation sensitivity, as adults show similar graded sensitivity [@Bailey2005].

@@

We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list. This process yielded 110 items. We then used the Google Scholar search engine to search for papers citing the original @Swingley2000 publication. This search was conducted on 22 September, 2017 and yielded 288 results. We removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech. The final sample (*n* = `r length(unique(descriptive_dat$short_cite))`) consisted of `r with(descriptive_dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "dissertation"]))` theses, and `r with(descriptive_dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports. We will refer to these items collectively as papers. Table \@ref(tab:SummaryTable) provides an overview of all papers included in the present meta-analysis.

@@

Mispronunciation sensitivity studies are typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement. PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images. Across papers the baseline comparison varied; since other options were not available to us, we used the baseline reported by the authors of each paper. Over half of the records (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post_naming_effect"])`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase, resulting in a Difference Score. The Difference Score is one value, which is then compared with a chance value of 0. Pre vs. Post (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` records) accomplishes the same analysis, directly compare the post- and pre-naming PTL scores with one another using a statistical test (e.g. t-test, ANOVA). This requires two values, one for the pre-naming phase and one for the post-naming phase. The remaining records used a Post dependent variable (*n* = `r with(dv_info, n_exp_conditions[within_measure == "post"])` records), which compares the post-naming PTL score with a chance value of 50%. Here, the infants' pre-naming phase baseline preferences are not considered and instead target fixations are evaluated based on the likelihood to fixate one of two pictures (50%). Standardized effect sizes based on mean differences, as calculated here, preserve the sign. Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more looks to the target.

@@

#Get standard errors from variances
new.dat$se = sqrt(new.dat$vi)
#Calculate 95% CI values
new.dat$lowerci = (-1.96*new.dat$se)+new.dat$yi
new.dat$upperci = (1.96*new.dat$se)+new.dat$yi
#Themes and plot
apatheme2=theme_bw()+
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.border=element_blank(),
        axis.line=element_line(),
        text=element_text(family='Times'),
        legend.position='none')
p=
  ggplot(new.dat, aes(y=reorder(study_ref, -yi), x=yi, xmin=lowerci, xmax=upperci))+
  #Add data points and color them black
  geom_point(color = 'black')+
  #Add 'special' points for the summary estimates, by making them diamond shaped
#  geom_point(data=subset(dat, tester=='Summary'), color='black', shape=18, size=4)+
  #add the CI error bars
  geom_errorbarh(height=.1)+
  #Specify the limits of the x-axis and relabel it to something more meaningful
  #scale_x_continuous(limits=c(-1.5,1.5), name='Standardized Mean Difference (g)')+
  #Give y-axis a meaningful label
  ylab('Reference')+
  #Add a vertical dashed line indicating an effect size of zero, for reference
  geom_vline(xintercept=0, color='grey', linetype='dashed')+
  #Add a vertical line to show mean effect
  geom_vline(xintercept=mean_correct, color='orange', linetype='dashed')+
    geom_vline(xintercept=mean_misp, color='blue', linetype='dashed')+
  #Create sub-plots (i.e., facets) based on levels of setting
  #And allow them to have their own unique axes (so authors don't redundantly repeat)
  facet_grid(condition~., scales= 'free', space='free')+
  #Apply my APA theme
  apatheme2
#p

@@

```{r PlotMPEffect, echo = FALSE, fig.width=7,fig.height=7, fig.cap="Panel a: Effect sizes for correct pronunciations (orange) and mispronunciations (blue) by participant age. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) by participant age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}

@@

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  ggtitle("a. Object Recognition")+
  geom_point(aes(size = weights_g),show.legend=FALSE, alpha = .5) + 
  geom_segment(aes(x = 6, y = 0, xend = 31, yend = 0), linetype="dotted", color = "black")+
  #geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_colour_grey()+
  xlim(6, 31) +
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Hedges' g")

@@

p.diff <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity)) + 
  ggtitle("b. Mispronunciation Sensitivity")+
  geom_point(aes(size = weight),show.legend=FALSE, alpha = .3) + 
  geom_segment(aes(x = 6, y = 0, xend = 31, yend = 0), linetype="dotted", color = "black")+
  #geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1), color = "black") +
  scale_colour_grey()+
  xlim(6, 31) +
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Hedges' g")

@@

  jpeg(filename = "figures/Figure_3_AgeEffect.jpg", 
       width = 500, height = 700, units = "px")

@@

```{r Vocabdescribe1, echo = FALSE, fig.width=7,fig.height=4.5, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (orange), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (green).", results="hide"}
#how did vocabulary collection change over time?

@@

vocab_year <- ggplot(d.v,aes(x=Year, fill = relationship)) + 
  apatheme+
  geom_histogram(alpha = 0.5, bins = 20) +
    scale_fill_grey()+
     theme(legend.position = "bottom",
           legend.title = element_blank())

@@

p.MS <- ggplot(dat.f, aes(Features_changed, g_calc, fill = Features_changed)) + 
  geom_violin() + 
  geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_grey()+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Hedges' g")

@@

ms.age <- ggplot(dat.f, aes(mean_age_1/30.44, g_calc, color = Features_changed)) + 
    #facet_grid(.~dv_label)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  scale_colour_grey()+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Hedges' g")

@@

ms.agg <- ggplot(dat.cm, aes(location_label, Misp_sensitivity, fill = location_label)) + 
  #facet_grid(.~dv_label)+
    geom_violin() + 
    geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_grey()+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Misp. Sensitivity")

@@

ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = location_label)) + 
    #facet_grid(.~dv_label)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  scale_colour_grey()+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Misp. Sensitivity")

@@

ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
  #facet_grid(.~dv_label)+
    geom_violin() + 
    geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_grey()+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Misp. Sensitivity")

ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = type_label)) + 
    #facet_grid(.~dv_label)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  scale_colour_grey()+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Misp. Sensitivity")

@@

  jpeg(filename = "figures/Figure_8_CV.jpg",
       width = 500, height = 600, units = "px")

@@

ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
  facet_grid(.~lang_family)+
    geom_violin() + 
  geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_grey()+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Hedges' g")

ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = type_label)) + 
  facet_grid(.~lang_family)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  scale_colour_grey()+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Hedges' g")

@@

  jpeg(filename = "figures/Figure_9_LangCV.jpg",
       width = 500, height = 900, units = "px")

@@

ms.agg <- ggplot(dat.cm, aes(distractor_label, Misp_sensitivity, fill = distractor_label)) + 
  #facet_grid(.~dv_label)+
    geom_violin() + 
    geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_grey()+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Misp. Sensitivity")

ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = distractor_label)) + 
    #facet_grid(.~dv_label)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  scale_colour_grey()+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Misp. Sensitivity")

@@

  jpeg(filename = "figures/Figure_6_Distractor_Overlap.jpg",
       width = 500, height = 600, units = "px")

@@

The developmental trajectory of mispronunciation sensitivity was influenced by type of mispronunciation and overlap between the target and distractor labels, but mispronunciation size, mispronunciation position, and distractor familiarity were found to have no influence. Finally, in some cases there was evidence that older and younger infants were given experimental manipulations that may have rendered the experimental task more or less difficult. In one instance, younger infants were given a more difficult task, mispronunciations on the medial position, which is unlikely to contribute to the lack of developmental effects in our main analysis. Yet, this was not always the case; in a different instance, older children were more likely to be given target-distractor pairs that overlapped on their onset phoneme, a situation in which it is more difficult to detect a mispronunciation and may have bearing on our main developmental results. We return to these findings in the General Discussion.

@@

We next considered whether an effect of maturation might have been masked by other factors we have not yet captured in our analyses. A strong candidate that emerged during the construction of the present dataset and careful reading of the original papers was the analysis approach. We observed, as mentioned in the Methods section, variation in the dependent variable reported, and additionally noted that the size of the chosen post-naming analysis window varied substantially across papers. Researchers' analysis strategy may be adapted to infants' age or influenced by having observed the data. For example, consider the possibility that a particular study does not find that infants looked to the target object upon hearing a correct pronunciation. With this pattern of behavior, interpreting an effect of mispronunciation sensitivity becomes difficult; how can infants notice a phoneme change when they do not even show recognition of the correct pronunciation? A lack of recognition or a small effect for correct pronunciations would be more difficult to publish [@Ferguson2012]. In order to have publishable results, adjustments to the analysis approach could be made until a significant effect of recognition for correct pronunciations is found. But, these adjustments would also need to be made for the analysis of mispronunciations, which may impact the size of the mispronunciation sensitivity effect. Such a scenario could explain the publication bias suggested by the asymmetry for correct pronunciations in the funnel plot shown in Figure \@ref(fig:FunnelCombo) [@Simmons2011]. This could lead to an increase in significant results and even alter the developmental trajectory of mispronunciation sensitivity.

>>>>

An *increase* in mispronunciation sensitivity with age is predicted by a maturation from holistic to more detailed phono-lexical representations and has been supported by several studies [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010]. The first words that infants learn are often not similar sounding [e.g. mama, ball, kitty; @CharlesLuce1995] and encoding representations for these words using fine phonological detail may not be necessary. According to PRIMIR [@Curtin2007; @Werker2005] infants' initial episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task. This argument is supported by the results of @Mani2010kepstups, who found that 12-month-old infants with a larger vocabulary showed a greater sensitivity to vowel mispronunciations than infants with a smaller vocabulary.

@@

The first set of questions concerns how infants' sensitivity is modulated by different kinds of mispronunciations. Following on the above example, some experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level, or *mispronunciation size* (i.e. 1-feature, 2-features, 3-features), finding that infants are more sensitive to larger mispronunciations (3-feature-changes) than smaller mispronunciations (1-feature changes) for both consonant [@White2008; @Bernier2017; @Tamasi2016] and vowel [@Mani2011] mispronunciations, known as graded sensitivity. By aggregating studies testing infants of different ages on mispronunciations of varying size, this also has consequences for understanding whether graded sensitivity changes over development.

@@

We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list (see Figure \@ref(fig:PRISMA-image) for an overview of the selection process). This process yielded 110 items. We then used the Google Scholar search engine to search for papers citing the original @Swingley2000 publication. This search was conducted on 22 September, 2017 and yielded 288 results. From this combined list of 398 records we removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech. The final sample (*n* = `r length(unique(descriptive_dat$short_cite))`) consisted of `r with(descriptive_dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "dissertation"]))` theses, and `r with(descriptive_dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports. We will refer to these items collectively as papers. Table \@ref(tab:SummaryTable) provides an overview of all papers included in the present meta-analysis.

@@

Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement. PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images. Across papers the baseline comparison varied; since other options were not available to us, we used the baseline reported by the authors of each paper. Over half of the records (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post_naming_effect"])`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase, resulting in a Difference Score. The Difference Score is one value, which is then compared with a chance value of 0. Pre vs. Post (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` records) accomplishes the same analysis, directly compare the post- and pre-naming PTL scores with one another using a statistical test (e.g. t-test, ANOVA). This requires two values, one for the pre-naming phase and one for the post-naming phase. The remaining records used a Post dependent variable (*n* = `r with(dv_info, n_exp_conditions[within_measure == "post"])` records), which compares the post-naming PTL score with a chance value of 50%. Here, the infants' pre-naming phase baseline preferences are not considered and instead target fixations are evaluated based on the likelihood to fixate one of two pictures (50%). Standardized effect sizes based on mean differences, as calculated here, preserve the sign. Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more looks to the target.

@@

#Get standard errors from variances
new.dat$se = sqrt(new.dat$vi)
#Calculate 95% CI values
new.dat$lowerci = (-1.96*new.dat$se)+new.dat$yi
new.dat$upperci = (1.96*new.dat$se)+new.dat$yi
#Themes and plot
apatheme2=theme_bw()+
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.border=element_blank(),
        axis.line=element_line(),
        text=element_text(family='Times'),
        legend.position='none')
p=
  ggplot(new.dat, aes(y=reorder(study_ref, -yi), x=yi, xmin=lowerci, xmax=upperci))+
  #Add data points and color them black
  geom_point(color = 'black')+
  #Add 'special' points for the summary estimates, by making them diamond shaped
#  geom_point(data=subset(dat, tester=='Summary'), color='black', shape=18, size=4)+
  #add the CI error bars
  geom_errorbarh(height=.1)+
  #Specify the limits of the x-axis and relabel it to something more meaningful
  #scale_x_continuous(limits=c(-1.5,1.5), name='Standardized Mean Difference (g)')+
  #Give y-axis a meaningful label
  ylab('Reference')+
  #Add a vertical dashed line indicating an effect size of zero, for reference
  geom_vline(xintercept=0, color='grey', linetype='dashed')+
  #Add a vertical line to show mean effect
  geom_vline(xintercept=mean_correct, color='yellow', linetype='dashed')+
    geom_vline(xintercept=mean_misp, color='blue', linetype='dashed')+
  #Create sub-plots (i.e., facets) based on levels of setting
  #And allow them to have their own unique axes (so authors don't redundantly repeat)
  facet_grid(condition~., scales= 'free', space='free')+
  #Apply my APA theme
  apatheme2
#p

@@

```{r PlotMPEffect, echo = FALSE, fig.width=7,fig.height=8, fig.cap="Panel a: Effect sizes for correct pronunciations (yellow) and mispronunciations (blue) by participant age. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) by participant age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}

@@

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  ggtitle("a.")+
  geom_point(aes(size = weights_g),show.legend=FALSE, alpha = .5) + 
  geom_segment(aes(x = 6, y = 0, xend = 31, yend = 0), linetype="dotted", color = "black")+
  #geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  #scale_colour_grey()+
    scale_color_manual(values=cbPalette)+
  xlim(6, 31) +
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        plot.title = element_text(size = 20)) + 
  xlab("Age in months") + 
  ylab("Hedges' g")

@@

p.diff <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity)) + 
  ggtitle("b.")+
  geom_point(aes(size = weight),show.legend=FALSE, alpha = .3) + 
  geom_segment(aes(x = 6, y = 0, xend = 31, yend = 0), linetype="dotted", color = "black")+
  #geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1), color = "black") +
  #scale_colour_grey()+
  scale_color_manual(values=cbPalette)+
  xlim(6, 31) +
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        plot.title = element_text(size = 20)) + 
  xlab("Age in months") + 
  ylab("Hedges' g")

@@

lay <- rbind(c(1),
             c(1),
             c(1),
             c(2),
             c(2))
#lay <- rbind(c(1,2))

  jpeg(filename = "figures/Figure_3_AgeEffect.jpg", 
       width = 500, height = 900, units = "px")

@@

```{r Vocabdescribe1, echo = FALSE, fig.width=7,fig.height=4.5, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (yellow), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (pink).", results="hide"}
#how did vocabulary collection change over time?

@@

vocab_year <- ggplot(d.v,aes(x=Year, fill = relationship)) + 
  apatheme+
  geom_histogram(alpha = 0.5, bins = 20) +
    #scale_fill_grey()+
    scale_fill_manual(values=cbPalette)+
     theme(legend.position = "bottom",
           legend.title = element_blank())

@@

p.MS <- ggplot(dat.f, aes(Features_changed, g_calc, fill = Features_changed)) + 
  geom_violin() + 
  geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  #scale_fill_grey()+
    scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Hedges' g")

@@

ms.age <- ggplot(dat.f, aes(mean_age_1/30.44, g_calc, color = Features_changed)) + 
    #facet_grid(.~dv_label)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  #scale_colour_grey()+
    scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Hedges' g")

@@

ms.agg <- ggplot(dat.cm, aes(location_label, Misp_sensitivity, fill = location_label)) + 
  #facet_grid(.~dv_label)+
    geom_violin() + 
    geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  #labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  #scale_fill_grey()+
    scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Misp. Sensitivity")

@@

ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = location_label)) + 
    #facet_grid(.~dv_label)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  #scale_colour_grey()+
    scale_color_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Misp. Sensitivity")

@@

ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
  #facet_grid(.~dv_label)+
    geom_violin() + 
    geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  #scale_fill_grey()+
    scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Misp. Sensitivity")

ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = type_label)) + 
    #facet_grid(.~dv_label)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  #scale_colour_grey()+
    scale_color_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Misp. Sensitivity")

@@

  jpeg(filename = "figures/Figure_7_CV.jpg",
       width = 500, height = 800, units = "px")

@@

ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
  facet_grid(.~lang_family)+
    geom_violin() + 
  geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  #scale_fill_grey()+
    scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Hedges' g")

ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = type_label)) + 
  facet_grid(.~lang_family)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  #scale_colour_grey()+
    scale_color_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Hedges' g")

@@

  jpeg(filename = "figures/Figure_8_LangCV.jpg",
       width = 500, height = 900, units = "px")

@@

ms.agg <- ggplot(dat.cm, aes(distractor_label, Misp_sensitivity, fill = distractor_label)) + 
  #facet_grid(.~dv_label)+
    geom_violin() + 
    geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  #scale_fill_grey()+
    scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Misp. Sensitivity")

ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = distractor_label)) + 
    #facet_grid(.~dv_label)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  #scale_colour_grey()+
    scale_color_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Misp. Sensitivity")

@@

  jpeg(filename = "figures/Figure_9_Distractor_Overlap.jpg",
       width = 500, height = 800, units = "px")

@@

When age was added as a moderator, mispronunciation sensitivity was found to vary by type of mispronunciation and overlap between the target and distractor labels over development, but age did not influence sensitivity to mispronunciation size, mispronunciation position, and distractor familiarity. Finally, in some cases there was evidence that older and younger infants were given experimental manipulations that may have rendered the experimental task more or less difficult. In one instance, younger infants were given a more difficult task, mispronunciations on the medial position, which is unlikely to contribute to the lack of developmental effects in our main analysis. Yet, this was not always the case; in a different instance, older children were more likely to be given target-distractor pairs that overlapped on their onset phoneme, a situation in which it is more difficult to detect a mispronunciation and may have bearing on our main developmental results. We return to these findings in the General Discussion.

@@

We next considered whether an effect of maturation might have been masked by other factors we have not yet captured in our analyses. A strong candidate that emerged during the construction of the present dataset and careful reading of the original papers was the analysis approach. We observed, as mentioned in the Methods section, variation in the dependent variable reported, and additionally noted that the size of the chosen post-naming analysis window varied substantially across papers. Researchers' analysis strategy may be adapted to infants' age or influenced by having observed the data. For example, consider the possibility that a particular study does not find that infants looked to the target object upon hearing a correct pronunciation. With this pattern of behavior, interpreting an effect of mispronunciation sensitivity becomes difficult; how can infants notice a phoneme change when they do not even show recognition of the correct pronunciation? A lack of recognition or a small effect for correct pronunciations would be more difficult to publish [@Ferguson2012]. In order to have publishable results, adjustments to the analysis approach could be made until a significant effect of recognition for correct pronunciations is found. But, these adjustments would also need to be made for the analysis of mispronunciations, which may impact the size of the mispronunciation sensitivity effect. Such a scenario could explain the publication bias suggested by the asymmetry for correct pronunciations in the funnel plot shown in Figure \@ref(fig:FunnelCombo) [@Simmons2011]. This could lead to an increase in significant results and even alter the apparent developmental trajectory of mispronunciation sensitivity measured in experiments.
